---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rfars

This is a package developed for the course "Building R Packages" on Coursera, as part of the Mastering Software Development in R specialization offered by Johns Hopkins University. It consists of a set of functions used to analyze and visualize the data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS).

This R package is available on Github and can be installed by calling the following function in R:

devtools::install_github("https://github.com/schwarja209/rfars")


##Purpose

The aim of this project was to combine the skills of creating, writing, and testing an R package, using the R files provided in the course Building R Packages offered by the Johns Hopkins University through the Coursera's platform.

For this assessment, it was required that we perform the following tasks:

- Write a vignette to be included in the package using knitr and R Markdown;
- Formulate at least one test using the testthat package;
- Put the package on Github;
- Set up the package's repository so that can be checked and built on Travis;
- Add the Travis badge to the package's README.md file, as soon as your package has built on Travis and the build is passing without errors, warnings, or notes.


## Example

The functions in rfars can be used as follows (using raw test data in the "data-raw" folder):

```{r example, eval=FALSE, comment=""}
fars_read(filename="accident_2013.csv.bz2")

make_filename(year=2013)

fars_read_years(years=c(2013,2014,2015))

fars_summarize_years(years=c(2013,2014,2015))

fars_map_state(state.num=1,year=2013)
```

Help files describing what each function does with the given inputs can be found in the "man" folder.


## R Session

The session in which I have created this package was the following:

```{r appendix, echo=FALSE, comment=""}
sessionInfo()
```
