---
title: "Using rfars"
author: "Jacob Schwartz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using rfars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

##Description

The rfars package bundles a set of functions to analyze the data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS).

##Usage Demos

###Getting the data into a more manageable format

The function `fars_read()` allows you to extract the data (samples in the "data-raw" folder) from a compressed format, and store it in a special R object.

```{r func1, eval=FALSE, comment=""}
# Extracts the data from a compressed file.
library(rfars)
data_2013 <- fars_read("accident_2013.csv.bz2")
head(data_2013)
```

The `fars_read_years()` function does the same, but without having to name the entire file.  Just provide the year(s) of the data of interest!

*Note: the function `make_filename()` also exists, but is mostly just an intermediate function.*

###Summarizing the car fatalities

In order to get the total number of fatalities by month, you can use the `fars_summarize_years()` function, without even having to read in the raw data first (it does it for you)!

```{r func2, eval=FALSE, comment=""}
# Creates a table by month & year with the total number of fatalities in 2013 y 2014.
fars_summarize_years(c(2013, 2014))
```


###Visualizing the car fatalities by state

The function `fars_map_state()` creates a map with the car fatalities in a US state (or states, by number code) from a specific year (again, pre-reading in the data is not necessary, as the function does it for you!).

```{r func3, eval=FALSE, comment=""}
# Plots the car fatalities for the state of Florida (12) in 2015. 
fars_map_state(12, 2015)
```
